Modelling BCG vaccination in the UK

### 2019-12-06 rmds/10-model-results.Rmd
model results corrections

Data on non-UK born cases, which were imported into the model via the force of infection (Chapter \@ref(model-development)), were not available beyond 2015. To account for this a, age and year adjusted, Poisson regression model was used to forecast future TB incidence in the non-UK born with age treated as a categorical variable. As for years with data, uncertainty was introduced into these forecasts by assuming that non-UK born incidence rates were scaled using the fitted measurement error and normally distributed with a standard distribution based on the fitted measurement standard error (Chapter \@ref(model-fitting)).

>>>>

Data on non-UK born cases, which were imported into the model via the force of infection (Chapter \@ref(model-development)), were not available beyond 2015. To account for this an, age and year adjusted, Poisson regression model was used to forecast future TB incidence in the non-UK born with age treated as a categorical variable. As for years with data, uncertainty was introduced into these forecasts by assuming that non-UK born incidence rates were scaled using the fitted measurement error and normally distributed with a standard distribution based on the fitted measurement standard error (Chapter \@ref(model-fitting)).
